\documentclass{article}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[box,completemulti]{automultiplechoice}

\begin{document}

\element{qqs}{
\begin{question}{good choice}
  How many points would you like for this question?
  \begin{choices}
    \correctchoice{Maximum: 10}\scoring{10}
    \wrongchoice{Only 5}\scoring{5}
    \wrongchoice{Two will be enough}\scoring{2}
    \wrongchoice{None, thanks}\scoring{0}
  \end{choices}
\end{question}
}

\element{qqs}{
\begin{questionmult}{added}
  Get free points checking the following boxes:
  \begin{choices}
    \correctchoice{2 points}\scoring{b=2}
    \wrongchoice{One negative point!}\scoring{b=0,m=-1}
    \correctchoice{3 points}\scoring{b=3}
    \correctchoice{1 point}
    \correctchoice{Half point}\scoring{b=0.5}
  \end{choices}
\end{questionmult}
}

\element{qqs}{
\begin{questionmult}{3 or zero}\scoring{mz=3}
  Only a perfect response will be scored 3 points - otherwise, null score.
  \begin{choices}
    \wrongchoice{Wrong}
    \wrongchoice{Wrong}
    \correctchoice{Right}
    \correctchoice{Right}
  \end{choices}
\end{questionmult}
}

\element{qqs}{
\begin{questionmult}{all for 2}\scoring{haut=2}
  Perfect response scored 2 points, and give back one point for any error...
  \begin{choices}
    \correctchoice{Right}
    \correctchoice{This one is OK}
    \correctchoice{Yes!}
    \wrongchoice{False!}
    \wrongchoice{Don't check!}
  \end{choices}
\end{questionmult}
}

\element{qqs}{
\begin{question}{attention}\scoring{b=2}
  Some very bad answer yields here to a negative score (-2), but the correct answer is rewarded 2 points.
  \begin{choices}
    \correctchoice{Good!}
    \wrongchoice{Not correct}
    \wrongchoice{Not correct}
    \wrongchoice{Not correct}
    \wrongchoice{Very bad answer!}\scoring{-2}
  \end{choices}
\end{question}
}

\element{qqs}{
\begin{questionmult}{as you like}
  Choose how much points you need:
  \begin{choices}
    \correctchoice{You take two points here}\scoring{b=2}
    \wrongchoice{Check to give 3 points}\scoring{b=0,m=3}
    \correctchoice{Get one if checked, but give one if not}\scoring{m=-1}
  \end{choices}
\end{questionmult}
}

\element{qqs}{
\begin{questionmult}{03}
  \scoring{default.COMP=10,default.PROP=11,formula=(COMP==PROP ? 1 : 0)}
  \AMCdontAnnotate
  Name an important gas in the air and its percentage.
    \begin{choices}
      \wrongchoice{steam}
      \wrongchoice{gas}
      \correctchoice{nitrogen}\scoring{set.COMP=1}
      \wrongchoice{oxygen}\scoring{set.COMP=2}
      \wrongchoice{carbon dioxide}
      \wrongchoice{20\%}\scoring{set.PROP=2}
      \wrongchoice{40\%}
      \wrongchoice{60\%}
      \correctchoice{80\%}\scoring{set.PROP=1}
    \end{choices}
\end{questionmult}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\onecopy{20}{

\noindent{\bf QCM  \hfill Scoring strategy test}

\vspace*{.5cm}
\begin{minipage}{.4\linewidth}
\centering\large\bf Test\\ Jan. 2008\end{minipage}
\namefield{\fbox{\begin{minipage}{.5\linewidth}
Name:

\vspace*{.5cm}\dotfill
\vspace*{1mm}
\end{minipage}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setgroupmode{qqs}{withreplacement}

\insertgroup{qqs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

}

\end{document}