\documentclass{article}
\usepackage{multicol}

\usepackage[nowatermark]{automultiplechoice}
\usepackage{cleveref}

\begin{document}

\setdefaultgroupmode{withoutreplacement}

\element{geography}{
  \begin{question}{g:Ghana}\AMClabel{g:Ghana}\scoring{b=Geography}
    What is the capital of Ghana?
    \begin{choiceshoriz}
      \correctchoice{Accra}
      \wrongchoice{Addis Abeba}
      \wrongchoice{Ankara}
      \wrongchoice{Apia}
    \end{choiceshoriz}
  \end{question}
}

\element{geography}{
  \begin{question}{g:Thailand}\AMClabel{g:Thailand}\scoring{b=Geography}
    What is the capital of Thailand?
    \begin{choiceshoriz}
      \correctchoice{Bangkok}
      \wrongchoice{Banjul}
      \wrongchoice{Beijing}
      \wrongchoice{Beirut}
      \wrongchoice{Berlin}
    \end{choiceshoriz}
  \end{question}
}

\element{geography}{
  \begin{question}{g:Egypt}\AMClabel{g:Egypt}\scoring{b=Geography}
    What is the capital of Egypt?
    \begin{choices}
      \correctchoice{Cairo}
      \wrongchoice{Caracas}
      \wrongchoice{Cayenne}
      \wrongchoice{Chisinau}
      \wrongchoice{Conakry}
    \end{choices}
  \end{question}
}

\element{geography}{
  \begin{question}{g:Ireland}\AMClabel{g:Ireland}\scoring{b=Geography}
    What is the capital of Ireland?
    \begin{multicols}{3}
      \begin{choices}
        \correctchoice{Dublin}
        \wrongchoice{Dili}
        \wrongchoice{Djibouti}
        \wrongchoice{Doha}
        \wrongchoice{Dakar}
        \wrongchoice{Dhaka}
      \end{choices}
    \end{multicols}
  \end{question}
}

\element{history}{
  \begin{questionmult}{h:1901}\AMClabel{h:1901}\scoring{formula=(History*(NBC-NMC))}
    Which of the following events are taking place during the year
    1901?
    \begin{choices}
      \correctchoice{Funeral of Queen Victoria in London}
      \correctchoice{Official end of the Caste War of Yucat\'an}
      \wrongchoice{King George of Greece becomes absolute monarch of Crete}
      \wrongchoice{The first line of the Paris M\'etro is opened}
    \end{choices}
  \end{questionmult}
}

\element{history}{
  \begin{questionmult}{h:1850}\AMClabel{h:1850}\scoring{formula=(History*(NBC-NMC))}
    Which of the following events are taking place during the year
    1850?
    \begin{choices}
      \correctchoice{American Express is founded by Henry Wells \& William Fargo}
      \wrongchoice{Napoleon Bonaparte crosses the Alps and invades Italy}
      \wrongchoice{Kwang-su becomes emperor of China}
      \wrongchoice{First horse-drawn omnibuses established in London}
    \end{choices}
  \end{questionmult}
}

\element{history}{
  \begin{questionmult}{h:1971}\AMClabel{h:1971}\scoring{formula=(History*(NBC-NMC))}
    Which of the following events are taking place during the year
    1971?
    \begin{choices}
      \correctchoice{Apollo 14 lands on the Moon}
      \correctchoice{The Soviet Union launches Salyut 1}
      \correctchoice{Death of Louis Armstrong}
      \wrongchoice{The first commercial Concorde flight takes off}
    \end{choices}
  \end{questionmult}
}


\onecopy{3}{

\noindent{\bf AMC  \hfill SAMPLE TEST}

\vspace{2ex}

\fbox{\begin{minipage}{.9\linewidth}
{\AMCquestionNumberfalse
\def\AMCbeginQuestion##1##2{}
\begin{questionmult}{a:Choice}\QuestionIndicative

You have to answer to one of the two sections (geography or  history), not both. 

Mark your choice below

\begin{choiceshoriz}[o]\scoring{formula=0}
  \correctchoice{geography: \cref{\AMCstudentlabel{g:Ghana},\AMCstudentlabel{g:Thailand},%
  \AMCstudentlabel{g:Egypt},\AMCstudentlabel{g:Ireland}}}
  \scoring{setglobal.History=0,setglobal.Geography=1}
  %
    \correctchoice{history: \cref{\AMCstudentlabel{h:1901},\AMCstudentlabel{h:1850},\AMCstudentlabel{h:1971}}}
    \scoring{setglobal.History=1,setglobal.Geography=0}
 \end{choiceshoriz}
\end{questionmult}
}
\end{minipage}}

\vspace{3ex}

\insertgroup{geography}

\insertgroup{history}

}
\end{document}
