\documentclass[12pt,a4paper]{article}

\usepackage{csvsimple}%

\usepackage[bloc,separateanswersheet,completemulti]{automultiplechoice}

%%%%%%%%%%%%command
\newcommand{\Test}{%
%
\onecopy{1}{%

%%%beginning of the  header
\begin{center}
\noindent{}\fbox{\vspace*{3mm}
         \Large\bf\name{}~\forename{}\normalsize{}% 
          \vspace*{3mm}
      }
\end{center}


\noindent{\bf QCM  \hfill TEST}

\vspace*{.5cm}
\begin{minipage}{.4\linewidth}
  \centering\large\bf Test\\ Examination on Jan. 1st, 2008
\end{minipage}

\begin{center}\em
Duration : 10 minutes.

  No documents allowed. The use of electronic calculators is forbidden.

  Questions using the sign \multiSymbole{} may have
  zero, one or several correct answers.  Other questions have a single correct answer.

  Negative points may be attributed to \emph{very
    bad} answers.
\end{center}
\vspace{1ex}
%%% end of the header



\restituegroupe{general}

\clearpage

%\AMCcleardoublepage   

% \AMCaddpagesto{3}




%%% beginning of the test sheet header:    

\begin{center}

{\large\bf Answer sheet:}

\noindent{}\champnom{\fbox{%
         \Large\bf\name{}~\forename{}\normalsize{} 
          \vspace*{1mm}
      }}
\end{center}


\begin{center}
  \bf\em Answers must be given exclusively on this sheet: 
  answers given on the other sheets will be ignored.
\end{center}


\AMCassociation{\id}

\formulaire

%\AMCaddpagesto{3}

}%onecopy
}%Test

\begin{document}

%%%Options
\AMCrandomseed{1237893}

\def\AMCformQuestion#1{{\sc Question #1 :}}

\setdefaultgroupmode{withoutreplacement}
%%% end of Options

%%% groups

\element{general}{
  \begin{question}{prez}    
    Among the following persons, which one has ever been a President of the French Republic?
    \begin{choices}
      \correctchoice{René Coty}
      \wrongchoice{Alain Prost}
      \wrongchoice{Marcel Proust}
      \wrongchoice{Claude Monet}
    \end{choices}
  \end{question}
}

\element{general}{
  \begin{questionmult}{pref}    
    Among the following cities, which ones are French prefectures?
    \begin{choices}
      \correctchoice{Poitiers}
      \wrongchoice{Sainte-Menehould}
      \correctchoice{Avignon}
    \end{choices}
  \end{questionmult}
}

\element{general}{
  \begin{question}{nb-ue}
    How many different states were members of the European Union in Jan. 2009?
    \begin{choiceshoriz}[o]
      \wrongchoice{15}
      \wrongchoice{21}
      \wrongchoice{25}
      \correctchoice{27}
      \wrongchoice{31}
    \end{choiceshoriz}
  \end{question}
}
%%% end of groups

\csvreader[head to column names]{list.csv}{}{\Test}

\end{document}
