\documentclass[a4paper]{article}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[box,completemulti,separateanswersheet]{automultiplechoice}    
\begin{document}

\AMCrandomseed{1237893}

\def\AMCformQuestion#1{{\sc Question #1:}}    

\setdefaultgroupmode{withoutreplacement}

\element{general}{
  \begin{question}{prez}
    Among the following persons, which one has ever been a President of the French Republic?
    \begin{choices}
      \correctchoice{René Coty}
      \wrongchoice{Alain Prost}
      \wrongchoice{Marcel Proust}
      \wrongchoice{Claude Monet}
    \end{choices}
  \end{question}
}

\element{general}{
  \begin{questionmult}{pref}
    Among the following cities, which ones are French prefectures?
    \begin{choices}
      \correctchoice{Poitiers}
      \wrongchoice{Sainte-Menehould}
      \correctchoice{Avignon}
    \end{choices}
  \end{questionmult}
}

\element{general}{
  \begin{question}{nb-ue}
    How many different states were members of the European Union in Jan. 2009?
    \begin{choiceshoriz}[o]
      \wrongchoice{15}
      \wrongchoice{21}
      \wrongchoice{25}
      \correctchoice{27}
      \wrongchoice{31}
    \end{choiceshoriz}
  \end{question}
}

\onecopy{5}{

%%% beginning of the test sheet header:

\noindent{\bf QCM  \hfill TEST}

\vspace*{.5cm}
\begin{minipage}{.4\linewidth}
  \centering\large\bf Test\\ Examination on Jan. 1st, 2008
\end{minipage}

\begin{center}\em
Duration : 10 minutes.

  No documents allowed. The use of electronic calculators is forbidden.

  Questions using the sign \multiSymbole{} may have
  zero, one or several correct answers.  Other questions have a single correct answer.

  Negative points may be attributed to \emph{very
    bad} answers.

\end{center}
\vspace{1ex}

%%% end of the header

\insertgroup{general}

\AMCcleardoublepage    

% \AMCaddpagesto{3} 

\AMCformBegin    

%%% beginning of the answer sheet header

{\large\bf Answer sheet:}
\hfill \namefield{\fbox{    
    \begin{minipage}{.5\linewidth}
      Firstname and lastname:

      \vspace*{.5cm}\namefielddots  
      \vspace*{1mm}
    \end{minipage}
  }}

\begin{center}
  \bf\em Answers must be given exclusively on this sheet:
  answers given on the other sheets will be ignored.
\end{center}

%%% end of the answer sheet header

\AMCform    

% \AMCaddpagesto{5} 

}

\end{document}